% Chapter 1: Context

\chapter{Context}

\label{chapter01}

This is a project developed in \textit{\company} and evaluated by the \textit{\univname} as a Final Degree Project.
\\\\
The main goal of this project is creating a tool for \textit{\company} to ease the routes comparison by different parameters, taking into account values like \textbf{user demand} and \textbf{flights provided} by airlines.
\\\\
Using this comparison, flights advertisement could be improved according to user demand. The company could also develop complex software using the huge amount of data it will compare through an Application Programming Interface.
\\\\
\company\ have more than 75 million flights information and all its users queries. In order compare all the data available and get significant results, the software should take into account all possible risks working with Big Data frameworks.

\section{\company}

\company\cite{skyscanner_strategy} was formed in 2004 when a group of people was frustrated by the difficulties of finding cheap flights.
\\\\
In 12 years has evolved from a little office in the suburbs of Edinburgh to a world wide company with ten offices in seven different countries. Having more than 4 million visitors every day and more or less half a million pounds of revenue per day.
\\\\
Now, is one of the top travel fare aggregate website. In the next 5 years, \company\ wants to become the travel experience that people prefer to the myriad confusing and unconnected travel apps.
\\\\
This growth is possible thanks to the revenue \company\ gets from the App and Website, but how does this company make money? Does it get money from its adds as Google and other top tech companies do? Or it sells valuable information to its stakeholders such as user trends like Facebook or Twitter?
\\\\
Since \company\ does not actually sell the flights (or hotel rooms or car hires) it cannot take a percent of the purchase. \company\ serves to the user a lot of data from different providers and once the user has selected what he wants to buy, it is redirected to the provider website to finish the acquisition.
\\\\
The provider knows where the user comes from and they give a percent of the profit to \company.

\section{\tribe}

This tribe\cite{marketplace_engine_home} is one of the most important tribes in \company\footnote{Learn more about \textit{\nameref{company_structure}} in section ??}, its mission is to provide the most comprehensive and accurate flight inventory for \company\ and her partners with minimum latency.
\\\\
Its main goal is to evolve the search, pricing, routes and browse services to be horizontally scalable and set us up to build a lightning fast, super accurate and fully comprehensive flight search engine, enabling the traveler to instantly find the best flight at the best price with minimum effort.

\section{\squad}

DeLorean\cite{delorean_squad_home} is a squad of \tribe, its mission is to provide the best data and services around the routes, timetables and modes of transportation to go from one point on Earth to another.
\\\\
The squad now provides a very fast service that serves flights logistic information between a given origin and destination. Some information you can find in a route is the fight number, carriers, stops, date ranges, etc.