\chapter{\company\ structure} 

\label{appendix_a}

\company\ has a very horizontal structure, based on Spotify's\cite{culture_of_growth}.
\\\\
In the top of the company hierarchy there is Gareth Williams (CEO and Co-founder). Bellow the rest of CxOs: CCO, CTO, CPO, CFO, CLO and the Senior Executive Assistant. Then vice presidents, senior managers, managers and then developers and interns\cite{crew_chart}.
\\\\
Apart from this hierarchy structure, the whole team, except the CEO, CxOs and the Senior Executive Assistant, is mainly split in \textbf{Squads}, each of those belong to a \textbf{Tribes}. Apart from Squads and Tribes there are also Chapters, Guilds ans XBT'S\cite{how_skyscanner_works}.

\section*{Squad}

Are independent teams of no more than 8 people that are focused on delivering a core mission. Each squad has the freedom to act and be accountable to its mission.

\section*{Tribe}

Squads belong to a Tribe. The tribe will have an aligning mission linking to each squad's mission and is only achievable depending on the success of each squad. The Tribe lead is responsible for providing the right environment to deliver and providing direction. 

\section*{Chapters}

Are people who do similar work. This is a secondary home, and how people are line managed. Chapter leads are responsible for developing people and in tribe practices.

\section*{Guilds}

Are communities of interest of people who do not necessarily do similar work. It is people from across the business that want to share knowledge, tools, and word practices. 

\section*{XBT'S (cross business teams)}

XBTS' provide a platform to help solve business problems or opportunities with no natural home while giving all employees the ability to make an impact across any area of \company.